Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375

### 2015-01-21 papers/B1555_EdgeOn/B1555_letter.tex
rewrite on Intro and Discussion. Few references added.

	Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. Little perturbation in gravitational potential is sufficent to bring flux ratio anomalies in strong lensed systems. This makes flux ratio anomaly becomes a promising tool to detect dark matter substructures \citep{Dalal2002, N13}. In radio band, lensing images are not sensitive to micro lensing from stars, and one can also avoid severe dust extinction issue like in optical or infrared band. However, only small number of flux ratio anomalous systems in radio are avaliable for analysis. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach using narrow-line quasar emission \citep{N14} is capable to seek out more flux ratio anomalous systems for substructure analysis. All of these studies show that flux ratio anomalous lens systems are expected to bring a new insight to our understanding on structure formation.\\
	On the other hand, numerical simulations on structure formation haven't reach a concise conclusion on the cause of flux ratio anomaly \citep{Xu14}. There are other possiblities can give rise to flux ratio anomaly. Before gathering any satistics or serious analysis, we must fully consider those non-substructure effects. Otherwise it could affect the estimation of substructure mass and even give false signal when searching possible satellite candidates. Among those non-substructure effects, we are interested in the gravitational effect caused by structure of lens galaxy itself. Thus, infrared image with high spatial resolution is essential in our study.\\
	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. In the latest SHARP imaging, we found clear edge-on disk within some known flux ratio anomalous lenses. We model one system, B1555+375, with a center bulge and an edge-on disk, intending to probe the possibility of that structure from lens galaxy can cause flux ratio anomaly. We present the latest SHARP data in part 2, lens model of B1555 in part 3, and discussion in part 4.

@@

\section{Lens Modeling}
To model B1555+375, we use the lens modeling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides an excellent fit to the image positions (?? IS THIS TRUE?) but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this information, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk(SIE+Expdisk). The second model
consists of two SIE mass profiles, for bulge and disk
respectively. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.

\begin{figure}
\plotone{B1555_Kp.eps}
\plottwo{B1555_model.eps}{B1555_residue.eps}
\caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
Exponential disk is marked by the green ellipse in residue image. We believe strong dust extinction from the edge-on disk makes B and D no detection in infrared. Thus leaving two negative holes in our residue.\label{fig1}}
\end{figure}

@@

%%table3
\begin{table}
\begin{center}
\caption{Flux Ratios of B1555+375 Components.\label{tbl-3}}
\begin{tabular}{lllccc}
\tableline\tableline
				&Radio &Infrared  &Model-predicted\\
\tableline
A/B			&$1.8$ &$3.5$ &$1.7$  \\ 
A/C 		&$2.0$ &$1.0$ &$2.2$  \\
A/D			&$13.0$ &$5.4$ &$8.0$  \\
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Flux ratio between the merging double is much higher in infrared than in radio, which is believed to be caused by strong dust extinction from the edge-on disk.}
\end{center}
\end{table}

@@

\section{Discussion}
We have seen a similar flux ratio anomaly pattern in our edge-on disk lens model of B1555+375. The model predicted point source images also well matched with radio observation. Our modeling result indicates structures of lens galaxy itself can dominant flux ratio anomalies on lensing images. 
Our follow up will be explore more similar SHARP systems with flux ratio anomaly and a recognizable edge-on disk. As shown in Figure 3, the flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
We still have great expectation on the substructure searching approach from flux ratio anomaly by using strong lensing systems. At the meanwhile, we would like to draw some attention on other factors can cause flux ratio anomaly. These factors also give a clue of the structure and mass distribution of lens galaxy, which can be important to research required really accurate measurements, like time-delay.  For substructure searching, one should reconsider and rule out the possibility of edge-on disk before doing any further analysis.\\
Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems.

>>>>

	Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. Little perturbation in gravitational potential is sufficent to bring flux ratio anomalies in strong lensed systems. This makes flux ratio anomaly becomes a promising tool to detect dark matter substructures \citep{Dalal2002, N13}. In radio band, lensing images are not sensitive to micro lensing from stars, and one can also avoid severe dust extinction issue like in optical or infrared band. However, only small number of flux ratio anomalous systems in radio are avaliable for analysis. Besides waiting for future large-scale survey such as LSST to find thousands of more new lens galaxies, another approach using narrow-line quasar emission \citep{N14} is capable to seek out more flux ratio anomalous systems for substructure analysis.

	With expected growth in the number of samples, several groups have developed the technique to estimate the properties of substructures from flux ratio anomalous systems. \citet{V09, H13} both analyze the strong lens imaging to detect substructures lie infront of Einstein ring. Their methods improve the detectable mass limit and also show that high spatial resolution imaging is essential for the substructure study. On the other hand, numerical simulations on structure formation do not reach the concise conclusion on flux ratio anomalous systems. The latest study on the cause of flux anomalies from \citet{Xu14} shows the low probability of the existence of substructures in their studied systems.

	The Strong lensing at High Angular Resolution Program(SHARP) is a project aims on known quadruple and Einstein ring lensing systems \citep{SHARP12}. We obtain high-resoltion images from Keck adaptive optics(AO) and Hubble Space Telescope(HST) observations. To better understand the cause of flux ratio anomaly in strong lensing systems, we model B1555+375, one of the systems discussed in \citet{Xu14}, with the new information obtained from the latest SHARP infrared imaging. We present the latest SHARP data in part 2, lens model of B1555+375 in part 3, and discussion in part 4.

@@

\section{Lens Modeling}
To model B1555+375, we use the lens modeling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this information, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk(SIE+Expdisk). The second model
consists of two SIE mass profiles, for bulge and disk
respectively. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.
%These authors present a singular isothermal ellipsoid (SIE) model that
%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)

\begin{figure}
\plotone{B1555_Kp.eps}
\plottwo{B1555_model.eps}{B1555_residue.eps}
\caption{Left: SHARP K-band image of B1555+375 Middle: Lens model image generated by glafic Right: Residue image of B1555+375.\\
An edge-on disk can be seen in the center of SHARP K-band image. Exponential disk is marked by the green ellipse in residue image. We believe strong dust extinction from the edge-on disk makes B and D no detection in infrared. Thus leaving two negative holes in our residue.\label{fig1}}
\end{figure}

@@

%%table3
\begin{table}
\begin{center}
\caption{Flux Ratios of B1555+375 Components.\label{tbl-3}}
\begin{tabular}{lccccc}
\tableline\tableline
				&Radio &Infrared  &Model-predicted\\
\tableline
A/B			&$1.8$ &$3.5$ &$1.7$  \\ 
A/C 		&$2.0$ &$1.0$ &$2.2$  \\
A/D			&$13.0$ &$5.4$ &$8.0$  \\
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablecomments{Radio observation data quoted from Table 2 in \citet{Marlow}. Flux ratio between the merging double is much higher in infrared than in radio, which is believed to be caused by strong dust extinction from the edge-on disk.}
\end{center}
\end{table}

@@

\section{Discussion}
We present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modeling, substructure is not neccessary to exist to cause the observed flux ratio anomaly. This indicates the flux ratio anomaly in B1555+375 is resulted from the structure of lens galaxy itself, which is the edge-on disk seen in the SHARP infrared imaging. Our result is consistent with the conclusion from  \citet{Xu14}. Their simulation gives a low probability on the hypothesis that substructure causing flux anomaly in B1555+375.

With our discover in B155+375, we show that the lens galaxy structure can dominate the flux ratio anomalous phenomenon in strong lensing system. This leads to a more general reminder. Not all of the flux anomalies indicate the existence of substructures. One must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data and analysis. For the flux ratio anomalies caused by real dark matter substructures and dwarf galaxies, non-stucture effects would also influence the estimated mass and other derived properties. Thus, we would like to draw some attention on these non-substructure effects. Once we understand more about their role in flux anomalous phenomenon, we can be more confident on searching unseen dwarf galaxies and dark matter substructures by searching flux ratio anomalous systems.

Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems. The radio and narrow band observations are the best approaches to obtain accurate flux ratio data. However, optical and infrared imaging can provide more information on the structure of lens galaxy, which is also an important part in analyzing flux anomalous systems since we've shown that an edge-on disk can cause flux ratio anomaly. Our follow up will be explore more flux anomalous SHARP systems that we also notice a recognizable edge-on disk in the infrared imaging. As shown in Figure 3, the flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
